### 2021-11-09 Final Doc/Chapters/Chapter3.tex
Final Doc Finished - pre check

@@

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.45]{Figures/pause.png}
\caption{Pause Menu}
\label{pause}
\end{figure}

>>>>

\noindent The next tutorial is meant to get the user acclimated to using the air version of the \texttt{Dash()} function. Through this, multiple spherical objects were placed in this section and when the player collides with them a column is removed from in front of the portal of this section. The user is introduced to this mechanic by being corralled into one within the view of a similar column. There are also multiple signs within this section explaining the goal of this section. Figure \ref{moves} depicts the plan and final version of this tutorial.

@@

\noindent The final tutorial section developed was the enemy section. In this section, the user can make use of all other mechanics to get through this section. This involves wallrunning and simple platforming before being confronted with a larger enemy before the portal. Figure \ref{enemy} shows the plan and final version of this section.

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.3]{Figures/pause.png}
\caption{Pause Menu}
\label{pause}
\end{figure}
